Democratizing Secure Two-Party Computation

### 2017-10-12 OaklandSubmission/eval.tex

\subsection{Standard models}
\label{sec:shallow}
We consider three types of classifiers: linear, Naive Bayes, and decision trees. 
These classifiers are trained on the followinng data sets from the UCI  machine learning repository~\cite{uci}:
 the Wisconsin Breast Cancer data set, 
Credit Approval data set, Audiology (Standardized) data set, Nursery data set, and
ECG (electrocardiogram) classification data from~\cite{barni}.

@@

The results for Na\"{i}ve Bayes are in Table~\ref{tab:nb}. As before, $n$ denotes the length of the input feature vector $x=(x_1,\ldots,x_n)$ and $F$ is the number of possible values of each $x_i$.
Although, there are no multiplications in these benchmarks, these do have a significant number of comparisons that result in many boolean-and gates (13k/750k denote 13000/75000). 
Here, again columns 4 and 5 show the results reported in~\cite{shafindss}. We observe that \tool generated code has competitive performance on this task. This improvement is significant as~\cite{shafindss} uses custom designed protocols and we are executing a generic two party computation (2PC). Moreover,~\cite{shafindss} remarks that generic 2PC did not scale to the smallest of their Naive Bayes classifiers and they had to scale down the prediction task and there a Yao-based implementation was 500 times slower. We have shown that by using \tool, generic 2PC can scale to real prediction tasks and provide performance competitive with specialized protocols.

@@

\begin{table*}
\begin{tabular}{c|c|c|c|c|c |c|c|c|c|c|c}
Dataset & $n$ & $F$ & Prev. time (s) & Prev. Comm (Mb) & LAN time (s) & WAN time (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates  & LOC\\
\hline
Nursery & 5 & 9 & 1.5 & 0.2 & 0.1 & 0.4 & 0.6 & 13k & 0 & 73k & 50\\
\hline
Audiology & 24 & 70 & 3.9 & 2.0 & 1.5 & 2.9 & 37 & 750k & 0 & 4219k & 50\\
\hline
\end{tabular}

 \caption{Naive Bayes results}
 \label{tab:nb} 
\end{table*}

>>>>

\subsection{Standard models}
\label{sec:shallow}
We consider three types of classifiers: linear, Na\"{i}ve Bayes, and decision trees. 
These classifiers are trained on the followinng data sets from the UCI  machine learning repository~\cite{uci}:
 the Wisconsin Breast Cancer data set, 
Credit Approval data set, Audiology (Standardized) data set, Nursery data set, and
ECG (electrocardiogram) classification data from~\cite{barni}.

@@

The results for Na\"{i}ve Bayes are in Table~\ref{tab:nb}. As before, $d$ denotes the length of the input feature vector $x$ and $F$ is the number of possible values of $x_i$ for each $i \in [d]$.
Although, there are no multiplications in these benchmarks, these do have a significant number of comparisons (due to secret look-up) that result in many boolean-and gates (13k/750k denote 13000/75000). 
Here, again columns 4 and 5 show the results reported in~\cite{shafindss}. We observe that \tool generated code has competitive performance on this task. This improvement is significant as~\cite{shafindss} uses custom designed protocols and we are executing a generic two party computation (2PC). Moreover,~\cite{shafindss} remarks that generic 2PC did not scale to the smallest of their Naive Bayes classifiers and they had to scale down the prediction task and there a Yao-based implementation was 500 times slower. We have shown that by using \tool, generic 2PC can scale to real prediction tasks and provide performance competitive with specialized protocols.

@@

\begin{table*}
\begin{tabular}{c|c|c|c|c|c |c|c|c|c|c|c}
Dataset & $d$ & $F$ & Prev. time (s) & Prev. Comm (Mb) & LAN time (s) & WAN time (s) & Comm. (Mb)  & \#And & \#Mul & \#Gates  & LOC\\
\hline
Nursery & 5 & 9 & 1.5 & 0.2 & 0.1 & 0.4 & 0.6 & 13k & 0 & 73k & 50\\
\hline
Audiology & 24 & 70 & 3.9 & 2.0 & 1.5 & 2.9 & 37 & 750k & 0 & 4219k & 50\\
\hline
\end{tabular}

 \caption{Na\"{i}ve Bayes results}
 \label{tab:nb} 
\end{table*}
